### 2020-12-23 README.Rmd
minor update to github action workflow name and badge

<!-- badges: start -->
[![R-CMD-check, code coverage](https://github.com/skgallagher/EpiCompare/workflows/R-CMD-check,%20code%20coverage/badge.svg)](https://github.com/skgallagher/EpiCompare/actions)
<!-- [![Travis build status](https://travis-ci.org/skgallagher/EpiCompare.svg?branch=master)](https://travis-ci.org/skgallagher/EpiCompare) -->
[![codecov](https://codecov.io/gh/skgallagher/EpiCompare/branch/master/graph/badge.svg)](https://codecov.io/gh/skgallagher/EpiCompare)

>>>>

<!-- badges: start -->
[![R-CMD-check, code coverage](https://github.com/skgallagher/EpiCompare/workflows/R-CMD-check%20and%20code%20coverage/badge.svg)](https://github.com/skgallagher/EpiCompare/actions)
<!-- [![Travis build status](https://travis-ci.org/skgallagher/EpiCompare.svg?branch=master)](https://travis-ci.org/skgallagher/EpiCompare) -->
[![codecov](https://codecov.io/gh/skgallagher/EpiCompare/branch/master/graph/badge.svg)](https://codecov.io/gh/skgallagher/EpiCompare)
